\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Ju Lin}
% \address{ 4489 Oxford Lane \\ San Antonio, PA 90024  }
\address{ \href{https://github.com/soasme }{Github: soasme} \\ \href{http://www.soasme.com}{Blog: www.soasme.com}}
\address{ +64~$\cdot$~027~$\cdot$~545~$\cdot$~3988 \\ soasme@gmail.com}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Summary}
    { {\bf Ju Lin } has a wide knowledge of web application, DevOps and system administration. He is an expert in Python Programming, Operating System, and Unix Networking. He is a passionate learner with endless curiosity and enjoys jumping out of the comfort zone. }
  \end{rSection}

  \begin{rSection}{Experience}

    \begin{rSubsection}{Lipinshuo, Inc}{ May 2015 - September 2016 }{Tech Lead, Software Engineer }{Beijing, China}
    \item Project leadership and management. Capable of leading high performing teams under tough deadlines, to meet expectations of multiple customers externally or internally.
    \item System administration. Maintained configurations for Nginx, supervisord, gunicorn, etc.
    \item System architecture. Developed gateway and message queue applications to improve the scale and performance of the entire system.
    \item Continuous Delivery. Wrote packaging tool \href{https://github.com/soasme/beeper.py}{\textit{Beeper}} and deploying tool \href{https://github.com/liwushuo/fapistrano}{\textit{Fapistrano}}.
    \item Migrated from JPEG to WEBP. Reduced CDN bandwidth by 75\%.
    \item Developed a fully functional e-shop web application that drove 1k+ orders every day.
    \item Developed a spider application to scrap production information in other websites.
    \end{rSubsection}

    \begin{rSubsection}{ Douban Read }{ April 2013 - March 2015 }{ Product Development Engineer }{Beijing, China}
    \item Designed and implemented a new version of robust, testable, document-autogen APIs. Reduced network calls by 30\%.
    \item Extracted ORM manipulations with built-in cache mechanism, reducing model codes by 30\%.
    \item Wrote hundreds of py.test fixtures and thousands of test cases. Improved code coverage by 20\%.
    \item Maintained tens of CI jobs within Jenkins.
    \end{rSubsection}

    \begin{rSubsection}{Douban Book}{ June 2012 - April 2013 }{ Product Development Engineer }{Beijing, China}
    \item Participated on the rebuilding \& refactoring process of \href{book.douban.com}{\textit {Douban Book}}, which was visited by millions of users everyday. Decoupled this system from a monolithic one, to archive independent deployment.
    \item Replaced PTL template engine with Mako.  Released smoothly and bug-free, and reduced code by thousands of lines.
    \item Implemented a system synchronizing product price and inventory from almost all e-bookshops in China, such as AmazonCN, Jingdong, Dangdang, etc. There were nearly 16 million+ subjects updating every day.
    \end{rSubsection}

  \end{rSection}

  \begin{center}
  \textit{ Please refer to \href{http://www.linkedin.com/in/linju}{ my LinkedIn profile } for the complete list of work experience and references.}
  \textit{ http://www.linkedin.com/in/linju }
  \end{center}

  \newpage

  \begin{rSection}{Education}
    { \bf Jimei University  } \hfill {\em September 2008 - June 2012 } \\
    { Bachelor Degree in Software Engineering } \\
  \end{rSection}

  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer Languages & Python, Javascript, Java, C \\
      Protocols & TCP/IP, UDP, HTTP, HTTPS, WSGI \\
      APIs & REST, SOAP, JSON, XML \\
      Databases & MySQL, Sqlite, Redis, Mongodb, Beansdb \\
      Python Web Frameworks & Flask, Django, Tornado, Quixote, Celery \\
      Python ORMs & DjangoORM, SQLAlchemy \\
      Python Web Runtimes & Supervisord, Gunicorn, uWSGI, Nginx \\
      Javascript Frameworks & Angular, React \& Redux \\
      VCS & Git, SVN \\
      CIs & Jenkins, TravisCI \\
      Editors & Emacs, Vim, SublimeText, Atom \\
    \end{tabular}
  \end{rSection}

\end{document}
