%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document}

%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Ju Lin}{February 11, 1991}  % Your name and date of birth or subtitle

\noindent\href{mailto:soasme@gmail.com}{soasme@gmail.com}\bull
\textsmaller{+}64 027 545 3988\bull 
\href{https://github.com/soasme}{@soasme\textit{(Github)}}\bull
\href{http://www.soasme.com}{www.soasme.com(Blog)}\\ % Your URL
\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%   SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

\vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

\begin{multicols}{2}  % Start a two-column layout
  %\noindent \textit{A summary of your interests, achievements, history, topic of study or any other short summary of your professional life.}\\\\
  Lin Ju has a wide knowledge about web application, dev-ops and system administration. He experts at Python programming, Operating System, and Unix Networking. He is a passionate learner with endless curiosity, without fears of jumping out of the comfort zone.
\end{multicols}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section

\headedsection {
  \href{
    http://www.liwushuo.com
  } {
    Liwushuo
  }
} {
  \textsc{Beijing, China}
} {
  \headedsubsection {
    Tech Leader, Backend Engineer
  } {
    May '2015 -- Current
  } {
    \bodytext{
      \begin{itemize}
      \item Project leadership and management. Capable of leading high performing teams under tough deadlines, to meet expectations of multiple customers externally or internally.
      \item System administration, maintaining configuration of Nginx, supervisord, gunicorn, etc.
      \item System architecture, using gateway and message queue to improve the scale and performance of the entire system.
      \item Develop a full functional e-shop web application driven 1k+ orders every day.
      \end{itemize}
    }
  }
}

\headedsection {
  \href{
    http://read.douban.com
  } {
    Douban Read
  }
} {
  \textsc{Beijing, China}
} {
  \headedsubsection {
    Product Development Engineer
  } {
    Apr '2013 -- March '2015
  } {
    \bodytext{
      \begin{itemize}
      \item Design and implementing a new version of robust, testable, document-autogen API.
      \item Lead the refactoring project of extracting ORM manipulation with builtin cache mechanism, with 30\% codes reduced in Model layer.
      \item Maintain Jenkins CI system.
      \item Write hundreds of py.test fixtures helping making test much more readable and Several types of tests: unit test, api test, api v2 test, ajax interface test, page element validation, integration test based on selenium, thrift service test, python lint, etc. Help improving 20\% code coverage.
      \end{itemize}
    }
  }
}

\headedsection {
  \href{http://book.douban.com}{Douban Book}
} {
  \textsc{Beijing, China}
} {
  \headedsubsection {
    Product Development Engineer
  } {
    Jun '2012 -- Apr '2013
  } {
    \bodytext{
      \begin{itemize}
      \item Participating on the Rebuilding \& Refactoring process of book.douban.com which used by millions of users everyday. Decoupled book module from others to archive independent deployment.
      \item Replaced PTL template engine with Mako. Thousands lines of code fewer, and smoothly released without breaking anything.
      \item Implement a system synchronizing product price and inventory from almost all book e-shops in China, such as Amazon, Jingdong, Dangdang, etc. There are nearly 16+ million subjects updating every day.
      \end{itemize}
    }
  }
}

\begin{center}
  \textit{Please refer to \href{http://www.linkedin.com/in/linju}{my Linkedin profile} for the complete list of work experiences along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection {
  Jimei University
} {
  \textsc{Amoy, China}
} {
  \headedsubsection {
    Bachelor degree in Software Engineering
  } {
    2008 -- 2012
  } {
    \bodytext{
      programming languages (\acr{C\#}/\acr{Java}),
      Focussed on computer science(\acr{Data Structure}/\acr{Algorithm}),
      robot simulation(\acr{Graphic}/\acr{AI})
      and the semantic web technology stack (\acr{JSP}/\acr{.NET}/\acr{MSSQL}).
    }
  }
}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%   SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\inlineheadsection {
  Natural languages:
} {
  Mandarin Chinese\textit{(mother tongue)},
  English \textit{(full professional proficiency)}.
}

\inlineheadsection {
  Computer languages:
} {
  Python\textit{(Master)},
  Javascript\textit{(Master)},
  Java\textit{(prior experience)},
}

\inlineheadsection {
  Operating System:
} {
  Linux \textit{(expert in scripting, writing configurations)},
  OSX \textit{(expert, using it everyday)}.
}

\inlineheadsection {
  Technical specialties:
} {
  Routine system health monitoring, patching, upgrading.
  Profiling system bottleneck.
  Software design and implementation, with(in) a team.
  Solid knowledge of web technologies:\ \acr{Front end stack(\textit{React}, \textit{Angular})}, \acr{RESTful API}, \acr{Continouous Integration\textit{(Jenkins)}}, \acr{System Administration} and \acr{DevOps(\textit{ansible}, \textit{docker})}.
}


% \spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%   INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \roottitle{Interests} % Top level section

% \inlineheadsection {
%  Non-exhaustive and in alphabetical order:
% } {
%  Open source, game development, science, and vegetarian cooking.
% }


\end{document}
